---
title: "Sourcebook"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Factorial ANOVA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA, fig.path = "figures/")
```

```{r,include=FALSE}
library(EASI)
```

```{r,include=FALSE}
FactorA <- c(1, 1, 1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 2)
FactorB <- c(1, 1, 1, 1, 2, 2, 2, 2, 1, 1, 1, 1, 2, 2, 2, 2)
Outcome <- c(0, 0, 3, 5, 4, 7, 4, 9, 9, 6, 4, 9, 3, 6, 8, 3)
FactorA <- factor(FactorA, levels = c(1, 2), labels = c("A1", "A2"))
FactorB <- factor(FactorB, levels = c(1, 2), labels = c("B1", "B2"))
```

# EASI | Data Analysis

## Factorial ANOVA

Prior to the steps below, enter the data as appropriate for the analyses (described elsewhere).

### Obtaining Descriptive Statistics

Get the mean and standard deviation of the dependent variable for each of the levels. The "by" option tells EASI how to split the data.

```r
(Outcome~FactorA) |> describeMoments(by = FactorB)
```

### Obtaining Inferential Statistics

Get the analysis of variance source table.

```r
(Outcome~FactorA) |> describeFactorial(by = FactorB)
```

Test the main effects for statistical significance.

```r
(Outcome~FactorA) |> testFactorial(by = FactorB)
```

Get the proportion of variance accounted for by the main effects.

```r
(Outcome~FactorA) |> estimateFactorial(by = FactorB)
```
