---
title: "Sourcebook"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Mixed ANOVA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA, fig.path = "figures/")
```

```{r,include=FALSE}
library(EASI)
```

```{r,include=FALSE}
Factor <- c(rep(1, 4), rep(2, 4))
Outcome1 <- c(0, 0, 3, 5, 4, 7, 4, 9)
Outcome2 <- c(4, 7, 4, 9, 9, 6, 4, 9)
Factor <- factor(Factor, levels = c(1, 2), labels = c("Level1", "Level2"))
MixedData <- construct(Factor, Outcome1, Outcome2)
```

# EASI | Data Analysis

## Mixed ANOVA

Prior to the steps below, enter the data as appropriate for the analyses (described elsewhere).

### Obtaining Descriptive Statistics

Get the mean and standard deviation of the dependent variable for each of the levels. They are retain for use in the inferential statistics section below.

```{r}
(MixedData) |> focus(Outcome1, Outcome2) |> describeMoments(by = Factor) -> MixedMoments
(MixedData) |> focus(Outcome1, Outcome2) |> describeCorrelations(by = Factor) -> MixedCorr
MixedMoments
MixedCorr
```

### Obtaining Inferential Statistics

Get the analysis of variance source table.

```{r}
(MixedMoments) |> describeFactorial(MixedCorr)
```

Test the main effects for statistical significance.

```{r}
(MixedMoments) |> testFactorial(MixedCorr)
```

Get the proportion of variance accounted for by the main effects.

```{r}
(MixedMoments) |> estimateFactorial(MixedCorr)
```
