---
title: "Sourcebook"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Repeated Measures ANOVA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA, fig.path = "figures/")
```

```{r,include=FALSE}
library(EASI)
```

```{r,include=FALSE}
Outcome1 <- c(0, 0, 3, 5)
Outcome2 <- c(4, 7, 4, 9)
RepeatedData <- construct(Outcome1, Outcome2)
```

# EASI | Data Analysis

## Repeated Measures ANOVA

Prior to the steps below, enter the data as appropriate for the analyses (described elsewhere).

### Obtaining Descriptive Statistics

Get the means and standard deviations for the variables.

```{r}
(RepeatedData) |> describeMoments()
```

### Obtaining Inferential Statistics

Get the analysis of variance source table.

```{r}
(RepeatedData) |> describeEffect()
```

Test the main effect for statistical significance.

```{r}
(RepeatedData) |> testEffect()
```

Get the proportion of variance accounted for by the main effect.

```{r}
(RepeatedData) |> estimateEffect()
```
