---
title: "Sourcebook"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Standardized Scores}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
knitr::opts_chunk$set(fig.width = 7, fig.height = 7, comment = NA, fig.path = "figures/")
```

```{r,include=FALSE}
library(EASI)
```

```{r,include=FALSE}
Outcome <- c(0, 0, 3, 5, 4, 7, 4, 9)
```

# EASI | Data Analysis

## Standardized Scores

Prior to the steps below, enter the data as appropriate for the analyses (described elsewhere).

### Computing Transformations

Use a formula to calculate a new vector with the transformed scores. 

```{r}
trOutcome <- Outcome + 1
```

Create and display a the data set in a frame.

```{r}
construct(Outcome, trOutcome)
```

### Computing Standardized Scores

Create a new variable vector containing the standardized scores.

```{r}
zOutcome <- scale(Outcome)
```

Create and display the data set in a frame.

```{r}
construct(Outcome, trOutcome, zOutcome)
```
