---
title: "R | Data Analysis"
author: "Craig A. Wendorf"
site: bookdown::bookdown_site
output: bookdown::bs4_book
url: https://cwendorf.github.io/Sourcebook
description: This page provides instructions for data analysis in R.
---

# R | Data Analysis

## Frequencies

###  Obtaining a Frequency Distribution

Get the frequency distribution for the variable.

```{r}
FrequencyTable <- table(Outcome)
FrequencyTable
prop.table(FrequencyTable)
```

### Obtaining Descriptive Statistics

Get the percentiles for the variable.

```{r}
length(Outcome)
summary(Outcome)
```

## Descriptives

### Obtaining Descriptive Statistics

Get the mean, variance, and standard deviation for the variable.

```{r}
mean(Outcome)
var(Outcome)
sd(Outcome)
```

## Correlations

### Obtaining Descriptive Statistics

Get the means and standard deviations for the variables.

```{r}
mean(Outcome1)
sd(Outcome1)
mean(Outcome2)
sd(Outcome2)
```

Get the covariance and correlation matrix for the variables.

```{r}
cov(Outcome1,Outcome2)
cor(Outcome1,Outcome2)
```

### Obtaining Inferential Statistics

Get the correlation, its test for statistical significance, and its confidence interval.

```{r}
cor.test(Outcome1,Outcome2)
```

## Standardized Scores

### Computing Transformations

Use a formula to calculate a new vector with the transformed scores. 

```{r}
trOutcome <- Outcome+1
```

Create and display a data frame to view the data set.

```{r}
data.frame(Outcome,trOutcome)
```

### Computing Standardized Scores

Create a new variable vector containing the standardized scores.

```{r}
zOutcome <- scale(Outcome)
```

Create and display a data frame to view the data set.

```{r}
data.frame(Outcome,trOutcome,zOutcome)
```

## Confidence Intervals

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the variable.

```{r}
describeMeans(Outcome)
```

### Obtaining Inferential Statistics

Get the mean and its confidence interval.

```{r}
t.test(Outcome)$conf.int
```

## One Sample t Test

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the variable.

```{r}
mean(Outcome)
sd(Outcome)
```

### Obtaining Inferential Statistics

Test the mean difference for statistical significance and get its confidence interval.

```{r}
t.test(Outcome,mu=7)
```

## Paired Samples t Test

### Obtaining Descriptive Statistics

Get the means and standard deviations for the variables.

```{r}
mean(Outcome1)
sd(Outcome1)
mean(Outcome2)
sd(Outcome2)
```

### Obtaining Inferential Statistics

Test the mean difference for statistical significance and get its confidence interval.

```{r}
t.test(Outcome1-Outcome2,mu=0)
```

```{r}
t.test(Outcome1,Outcome2,paired=TRUE)
```

## Independent Samples t Test

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the dependent variable for each of the levels.

```{r}
by(Outcome,Factor,mean)
by(Outcome,Factor,sd)
```

### Obtaining Inferential Statistics

Test the mean difference for statistical significance and get its confidence interval.

```{r}
t.test(Outcome~Factor,var.equal=T)
```

## One Way ANOVA

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the dependent variable for each of the levels.

```{r}
by(Outcome,Factor,mean)
by(Outcome,Factor,sd)
```

```{r}
Results <- aov(Outcome~Factor)
model.tables(Results,"means")
```

### Obtaining Inferential Statistics

Get the analysis of variance source table with test of statistical significance.

```{r}
summary(Results)
```

## Post Hoc Comparisons

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the dependent variable for each of the levels.

```{r}
by(Outcome,Factor,mean)
by(Outcome,Factor,sd)
```

```{r}
Results <- aov(Outcome~Factor)
model.tables(Results,"means")
```

### Obtaining Inferential Statistics

Test each pairwise comparison for statistical significance.

```{r}
TukeyHSD(Results)
```

## Repeated Measures ANOVA

### Obtaining Descriptive Statistics

Get the means and standard deviations for the variables.

```{r}
mean(Outcome1)
sd(Outcome1)
mean(Outcome2)
sd(Outcome2)
```

Change data format for use with R procedures.

```{r}
StackData=reshape(RepeatedData,varying=c("Outcome1","Outcome2"),v.names="Outcome",timevar="Factor",idvar="Subject",direction="long")
attach(StackData)
StackData
```

```{r}
Results=aov(Outcome~factor(Factor)+Error(factor(Subject)))
model.tables(Results,"means")
```

### Obtaining Inferential Statistics

Get the ANOVA source table with tests of statistical significance.

```{r}
summary(Results)
```

## Factorial ANOVA

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the dependent variable for each of the levels.

```{r}
Results <- aov(Outcome~FactorA*FactorB)
model.tables(Results,"means")
```

### Obtaining Inferential Statistics

Get the analysis of variance source table with test of statistical significance.

```{r}
summary(Results)
```
