---
title: "EASI | Data Analysis"
author: "Craig A. Wendorf"
site: bookdown::bookdown_site
output: bookdown::bs4_book
url: https://cwendorf.github.io/Sourcebook
description: This page provides instructions for data analysis in EASI.
---

# EASI | Data Analysis

## Frequencies

###  Obtaining a Frequency Distribution

Get the frequency distribution for the variable.

```{r}
describeFrequencies(Outcome)
```

### Obtaining Descriptive Statistics

Get the percentiles for the variable.

```{r}
describePercentiles(Outcome)
```

## Descriptives

###  Obtaining a Frequency Distribution

Get the frequency distribution for the variable.

```{r}
describeFrequencies(Outcome)
```

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the variable.

```{r}
describeMeans(Outcome)
```

## Correlations

### Obtaining Descriptive Statistics

Get the means and standard deviations for the variables.

```{r}
describeMeans(CorrelationData)
```

Get the covariance matrix for the variables.

```{r}
describeCovariances(CorrelationData)
```

Get the correlation matrix for the variables.

```{r}
describeCorrelations(CorrelationData)
```

### Obtaining Inferential Statistics

Get the correlation and its confidence interval.

```{r}
estimateCorrelations(CorrelationData)
```

Test the correlation for statistical significance.

```{r}
testCorrelations(CorrelationData)
```

## Standardized Scores

### Computing Transformations

Use a formula to calculate a new vector with the transformed scores. 

```{r}
trOutcome <- Outcome+1
```

Create and display a data frame to view the data set.

```{r}
data.frame(Outcome,trOutcome)
```

### Computing Standardized Scores

Create a new variable vector containing the standardized scores.

```{r}
zOutcome <- scale(Outcome)
```

Create and display a data frame to view the data set.

```{r}
data.frame(Outcome,trOutcome,zOutcome)
```

## Confidence Intervals

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the variable.

```{r}
describeMeans(Outcome)
```

### Obtaining Inferential Statistics

Get the mean and its confidence interval.

```{r}
estimateMeans(Outcome)
```

## One Sample t Test

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the variable.

```{r}
describeMeans(Outcome)
```

### Obtaining Inferential Statistics

Get the mean difference and its confidence interval.

```{r}
estimateMeans(Outcome,mu=7)
```

Test the mean difference for statistical significance.

```{r}
testMeans(Outcome,mu=7)
```

Get the standardized effect size for the mean difference.

```{r}
estimateStandardizedMeans(Outcome,mu=7)
```

## Paired Samples t Test

### Obtaining Descriptive Statistics

Get the means and standard deviations for the variables.

```{r}
describeMeans(PairedData)
```

### Obtaining Inferential Statistics

Get the mean difference and its confidence interval.

```{r}
estimateMeanDifference(PairedData)
```

Test the mean difference for statistical significance.

```{r}
testMeanDifference(PairedData)
```

Get the standardized effect size for the mean difference.

```{r}
estimateStandardizedMeanDifference(PairedData)
```

## Independent Samples t Test

### Obtaining Descriptive Statistics

Get the mean and standard deviation of the dependent variable for each of the levels.

```{r}
describeMeans(Outcome~Factor)
```

### Obtaining Inferential Statistics

Get the mean difference and its confidence interval.

```{r}
estimateMeanDifference(Outcome~Factor)
```

Test the mean difference for statistical significance.

```{r}
testMeanDifference(Outcome~Factor)
```

Get the standardized effect size for the mean difference.

```{r}
estimateStandardizedMeanDifference(Outcome~Factor)
```

## One Way ANOVA

### Obtaining Descriptive Statistics

Get the mean and standard deviation of the dependent variable for each of the levels.

```{r}
describeMeans(Outcome~Factor)
```

### Obtaining Inferential Statistics

Get the analysis of variance source table.

```{r}
describeMeansOmnibus(Outcome~Factor)
```

Test the main effect for statistical significance.

```{r}
testMeansOmnibus(Outcome~Factor)
```

Get the proportion of variance accounted for by the main effect.

```{r}
estimateMeansOmnibus(Outcome~Factor)
```

## Post Hoc Comparisons

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the dependent variable for each of the levels.

```{r}
describeMeans(Outcome~Factor)
```

### Obtaining Inferential Statistics

Get all pairwise mean difference and their confidence intervals while adjusting them for multiple comparisons.

```{r}
estimateMeansPosthoc(Outcome~Factor)
```

Test all pairwise mean differences for statistical significance while adjusting them for multiple comparisons.

```{r}
testMeansPosthoc(Outcome~Factor)
```

Get standardized mean differences for all pairwise comparisons.

```{r}
estimateStandardizedMeansPosthoc(Outcome~Factor)
```

## Repeated Measures ANOVA

### Obtaining Descriptive Statistics

Get the means and standard deviations for the variables.

```{r}
describeMeans(RepeatedData)
```

### Obtaining Inferential Statistics

Get the analysis of variance source table.

```{r}
describeMeansOmnibus(RepeatedData)
```

Test the main effect for statistical significance.

```{r}
testMeansOmnibus(RepeatedData)
```

Get the proportion of variance accounted for by the main effect.

```{r}
estimateMeansOmnibus(RepeatedData)
```

## Factorial ANOVA

### Obtaining Descriptive Statistics

Get the mean and standard deviation of the dependent variable for each of the levels. The "by" option tells EASI how to split the data.

```r
describeMeansBy(Outcome~FactorA,by=FactorB)
```

### Obtaining Inferential Statistics

Get the analysis of variance source table.

```r
describeMeansOmnibusMultifactor(Outcome~FactorA,by=FactorB)
```

Test the main effects for statistical significance.

```r
testMeansOmnibusMultifactor(Outcome~FactorA,by=FactorB)
```

Get the proportion of variance accounted for by the main effects.

```r
estimateMeansOmnibusMultifactor(Outcome~FactorA,by=FactorB)
```
