---
title: "Sourcebook"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Factorial ANOVA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

# R | Data Analysis

## Factorial ANOVA

### Entering Data

Enter the data in vectors that assign variable names. Notice that each participant has scores on both the Factors and Outcome Variables. There will be as many scores as people. On the categorical Factors, you will use numbers to represent the categories (or “levels”) of the variables.

```{r}
FactorA <- c(1,1,1,1,1,1,1,1,2,2,2,2,2,2,2,2)
FactorB <- c(1,1,1,1,2,2,2,2,1,1,1,1,2,2,2,2)
Outcome <- c(0,0,3,5,4,7,4,9,9,6,4,9,3,6,8,3)
```

Declare which variables are considered Factors. In addition to specifying how many levels the factors have, you can provide labels for them.

```{r}
FactorA <- factor(FactorA,levels=c(1,2),labels=c("A1","A2"))
FactorB <- factor(FactorB,levels=c(1,2),labels=c("B1","B2"))
```

### Viewing Data

Create and display a data frame to view the data set.

```{r}
FactorialData <- data.frame(FactorA,FactorB,Outcome)
FactorialData
```

### Obtaining Descriptive Statistics

Get the mean, sample size, and standard deviation for the dependent variable for each of the levels. Also, get the means for the main effects.

```{r}
Results <- aov(Outcome~FactorA*FactorB)
model.tables(Results,"means")
tapply(Outcome, list(FactorA,FactorB), length)
tapply(Outcome, list(FactorA,FactorB), sd)
```

### Obtaining Inferential Statistics

Get the analysis of variance source table with test of statistical significance.

```{r}
summary(Results)
```
