---
title: "Statistics for Social Science"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Paired Sample t Test}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

## R: Paired Samples t Test

### Entering Data

Enter the data in vectors that assign variable names.

```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
```

### Viewing Data

Create and display a data frame to view the data set.

```{r}
PairedData <- data.frame(Outcome1,Outcome2)
PairedData
```

### Obtaining Descriptive Statistics

Get the means and standard deviations for the variables.

```{r}
mean(Outcome1)
sd(Outcome1)
mean(Outcome2)
sd(Outcome2)
```

### Obtaining Inferential Statistics

Test the mean difference for statistical significance and get its confidence interval.

```{r}
t.test(Outcome1-Outcome2,mu=0)
t.test(Outcome1-Outcome2,mu=0,conf.level=.99)
```

```{r}
t.test(Outcome1,Outcome2,paired=TRUE)
t.test(Outcome1,Outcome2,paired=TRUE,conf.level=.99)
```
