---
title: "Sourcebook"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Repeated Measures ANOVA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

# R | Data Analysis

## Repeated Measures ANOVA

### Entering Data

Enter the data in vectors that assign variable names.

```{r}
Outcome1 <- c(0,0,3,5)
Outcome2 <- c(4,7,4,9)
```

### Viewing Data

Create and display a data frame to view the data set.

```{r}
RepeatedData <- data.frame(Outcome1,Outcome2)
RepeatedData
```

### Obtaining Descriptive Statistics

Get the means and standard deviations for the variables.

```{r}
mean(Outcome1)
sd(Outcome1)
mean(Outcome2)
sd(Outcome2)
```

Change data format for use with R procedures.

```{r}
StackData=reshape(RepeatedData,varying=c("Outcome1","Outcome2"),v.names="Outcome",timevar="Factor",idvar="Subject",direction="long")
attach(StackData)
StackData
```

```{r}
Results=aov(Outcome~factor(Factor)+Error(factor(Subject)))
model.tables(Results,"means")
```

### Obtaining Inferential Statistics

Get the ANOVA source table with tests of statistical significance.

```{r}
summary(Results)
```
