---
title: "Sourcebook"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Repeated Measures ANOVA}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

# R | Data Analysis

## Repeated Measures ANOVA

### Entering Data

Enter the data in vectors that assign variable names.

```{r}
Outcome1 <- c(0, 0, 3, 5)
Outcome2 <- c(4, 7, 4, 9)
```

### Viewing Data

Create and display a data frame to view the data set.

```{r}
RepeatedData <- data.frame(Outcome1, Outcome2)
RepeatedData
```

### Reformat Data

Reformat the data from wide format to long format for analysis.

```{r}
Subject <- factor(rep(1:4, times = 2))
Time <- factor(rep(c("Time1", "Time2"), each = 4))
Outcome <- c(Outcome1, Outcome2)
```

### Obtaining Descriptive Statistics

Get the sample sizes, means, and standard deviations for the variables.

```{r}
Results <- aov(Outcome ~ Time + Error(Subject / Time))
model.tables(Results, "means")
lapply(
  split(Outcome, Time),
  function(x) c(n = length(x), mean = mean(x), sd = sd(x))
)
```

### Obtaining Inferential Statistics

Get the ANOVA source table with tests of statistical significance.

```{r}
summary(Results)
```
