---
title: "Sourcebook"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Standardized Scores}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

# R | Data Analysis

## Standardized Scores

### Entering Data

Enter the data in a vector that assigns a variable name.

```{r}
Outcome <- c(0,0,3,5,4,7,4,9)
```

### Viewing Data

Create and display a data frame to view the data set.

```{r}
StandardizedData <- data.frame(Outcome)
StandardizedData
```

### Computing Transformations

Use a formula to calculate a new vector with the transformed scores. 

```{r}
trOutcome <- Outcome+1
```

Create and display a data frame to view the data set.

```{r}
data.frame(Outcome,trOutcome)
```

### Computing Standardized Scores

Create a new variable vector containing the standardized scores.

```{r}
zOutcome <- scale(Outcome)
```

Create and display a data frame to view the data set.

```{r}
data.frame(Outcome,trOutcome,zOutcome)
```
