---
title: "Statistics for Social Science"
author: "Craig A. Wendorf"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    keep_md: TRUE
vignette: >
  %\VignetteIndexEntry{Post Hoc Tests}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r,include=FALSE}
#suppress the warnings and other messages from showing in the knitted file.
knitr::opts_chunk$set(fig.width=7, fig.height=5,fig.path='figures/',echo=TRUE,warning=FALSE,message=FALSE)
```

## Post Hoc Tests

### Entering Data

Enter the data in vectors that assign variable names. On the categorical Factors, you will use numbers to represent the categories (or “levels”) of the variable.

```{r}
Factor <- c(rep(1,4),rep(2,4),rep(3,4))
Outcome <- c(0,0,3,5,4,7,4,9,9,6,4,9)
```

Declare which variable is considered a Factor. In addition to specifying how many levels the factor has, you can provide labels for them.

```{r}
Factor <- factor(Factor,levels=c(1,2,3))
```

Create and display a data frame to view the data set.

```{r}
PostHocsData <- data.frame(Factor,Outcome)
PostHocsData
```

### Obtaining Descriptive Statistics

Get the mean and standard deviation for the dependent variable for each of the levels.

```{r}
by(Outcome,Factor,mean)
by(Outcome,Factor,sd)
```

```{r}
Results <- aov(Outcome~Factor)
model.tables(Results,"means")
```

### Obtaining Inferential Statistics

Test each pairwise comparison for statistical significance.

```{r}
TukeyHSD(Results)
```
